% adapted by WS from SSR's Word document and from the 5-part series at
% https://www.overleaf.com/learn/latex/How_to_Write_a_Thesis_in_LaTeX_(Part_1):_Basic_Structure
% reviewed by MAM

\documentclass[12pt,twosided]{report}

\usepackage[titletoc]{appendix} % for adding appendix to TOC
\usepackage{biblatex}  % reference management
\usepackage{geometry}  % better margins and margin control
\usepackage{graphicx}  % to include figures
\usepackage{hyperref}  % internal and external links
\usepackage[utf8]{inputenc}  % support for non-ASCII characters
\usepackage{listings}  % typset code
\usepackage{outlines}  % easy nesting of lists
\usepackage{tabularx}  % more control over table column width
\usepackage{titlesec}  % customize chapter title 
\usepackage{upquote}  % prevent mishandling of single quotes in listings
\usepackage{placeins}


% TODO: Customize the appearance of hyperref links using \hypersetup
% See https://en.wikibooks.org/wiki/LaTeX/Hyperlinks#Customization

% Custom format of chapter title.
\titleformat{\chapter}[hang]{\bf\huge}{\thechapter.}{2pc}{}

% Separate folder for images named 'images'.
\graphicspath{ {images/} }

% Separate file for references
\addbibresource{references.bib}

% Replace with your title
\title{The Third Space}

% Allow recalling document title
% from https://tex.stackexchange.com/a/15806/44301
\makeatletter\let\Title\@title\makeatother  

\begin{document}

\include{titlepage}  % title page.
\include{approval}  % approval page.

\chapter*{Dedication}
For ammi, abbu and all the hard-working people who try everyday to make the best of their abilities and earn a respectable living. You all are real heros because you know how to fight and live with dignity. May you earn the best of all your dedication and hard-work!

\chapter*{Acknowledgements}
We want to thank the Transgender community of Karachi in helping us get an insight on the distress the minorities communities face on regular basis.\\ We would like to thank the CS faculty for helping us transition through these difficult times since COVID 19 has impacted all of our lives in various ways.\\ Special mention for all the YouTube tutorials and computer-geek YouTubers like Mosh, bithoven, thecodeninja and all others that helped us pre-COVID 19 and all-through the lockdown to learn a whole development stack and apply it well to our project. We are proud to say that all code is written from scratch! (literally blank file!). This would not have been possible without their support.\\ Our supervisor, Nadia Nasir, is a gem of a person. Despite all the difficulties we faced, she always made time to listen to us, advise us, scold us and treat us like her own. Kudos for this strong woman!\\\\ Lastly, our beloved friends! They have been the major support throughout the ups and downs for the past four years, crying and cheering with us. The stress dealing would not have been possible without daily Tap-Catch games, random eatery trips, all the dhaaba chae sessions, bollywood movie screening, Aladin park rides, night stays with friends or memorable trips to Ziarat, Keenjhar Lake and Mubarak Village. Even during the lockdown, they never left our side and kept supporting us on daily basis through online games and video calls. Our deepest gratitude to all our beloved friends. Thank you so much for being a part of our life :')

\chapter*{Abstract}
This project is an e-commerce platform, which will work like a virtual mall. Every vendor will be having their own shop (profile) and every customer their shopping cart. This project is built with the sole purpose of providing employment opportunities to the skilled yet marginalized communities of this city and country. With this project we targeted two domains, i.e. Rights and Employment Opportunities for Marginalized communities and the market condition(s) of small-scale Arts and Crafts businesses in the age of rising E-Commerce industry.

% The following are automatically populated by LaTeX \chapter, \section and related, \figure, and \table.
\tableofcontents
\listoffigures
\listoftables

% TODO: Put chapters in a separate folder named 'chapters'.

\chapter{Introduction}
\label{chap:intro}
\input{chapters/introduction}

\chapter{Literature Review}
\label{chap:lit}
\input{chapters/review}

\chapter{Software Requirement Specification (SRS)}
\label{chap:srs}
\input{chapters/srs}

\chapter{Software Design Specification (SDS)}
\label{chap:sds}
\input{chapters/sds}

\chapter{Experiments and Results}
\label{chap:results}
\input{chapters/results}

\chapter{Conclusion and Future Work}
\label{chap:outro}
\input{chapters/conclusion}

\begin{appendices}

\titleformat{\chapter}[hang]{\bf\huge}{Appendix \thechapter.}{2pc}{}
% \titleformat{\chapter}[hang]{\bf\huge}{\thechapter.}{2pc}{}

  
% This appendix is optional.
%\chapter{More Math}
%\input{chapters/appendix-math}

% This appendix is required if the data set is not fully described in the main text.
\chapter{User Interface}
\input{chapters/appendix-data}

% This appendix is required if the code is not fully described in the main text.
\chapter{Code}
\input{chapters/appendix-code}
\end{appendices}

% Print the bibliography with a ToC entry and titled, "References".
\printbibliography[heading=bibintoc,title={References}]

\end{document}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:
